Cognate beginnings to bilingual lexical acquisition

### 2023-08-15 manuscript/manuscript.qmd
Fix affiliations and figure caption

```{r fig-marginal}
#| label: fig-marginal
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 4.5
#| out-width: 100%
#| eval: true
#| fig-cap: "Posterior marginal effects. Lines and error bands correspond to the mean and 95% credible interval of the posterior-predicted means. Different colours indicate different levels of cognateness (phonological similarity). Predictions are presented separately for different degrees of word-form exposure index: little exposure to the word-form, mean exposure, and high exposure). Predictions for Comprehension are shown on top and predictions for Comprehension and Production are shown on the bottom. In-sample predictions lie inside the grey rectangles."
fig_data <- model_epreds |>
    ungroup() |>
    reframe(
        .median = mean(.value),
        .lower = tidybayes::qi(.value, .width = 0.95)[, 1],
        .upper = tidybayes::qi(.value, .width = 0.95)[, 2],
        .by = c(ends_with("_std"), .category)
    ) |>
    mutate(
        age = (age_std * sd(responses$age)) + mean(responses$age),
        exposure = factor(exposure_std,
            levels = unique(exposure_std),
            labels = c(
                "Low exposure (-1 SD)",
                "Mean exposure",
                "High exposure (+1 SD)"
            ),
            ordered = TRUE
        ),
        lv = factor(lv_std,
            levels = unique(lv_std),
            labels = paste0(c(0, 50, 100), "%"),
            ordered = TRUE
        ),
        .category = ifelse(.category == "Understands",
            "Comprehension",
            "Production"
        )
    )
fig_data |>
    ggplot(aes(age, .median,
        ymin = .lower,
        ymax = .upper,
        colour = lv,
        fill = lv,
        linetype = lv
    )) +
    facet_grid(.category ~ exposure) +
    annotate(
        geom = "rect",
        xmin = min(responses$age),
        xmax = max(responses$age),
        ymin = -Inf,
        ymax = Inf,
        fill = "orange",
        alpha = 1 / 4,
        linetype = "dotted"
    ) +
    annotate(
        geom = "text",
        x = min(responses$age),
        y = 1,
        hjust = 0,
        vjust = 0.9,
        label = "Observed\nage range",
        size = 2
    ) +
    geom_vline(
        xintercept = mean(responses$age),
        linewidth = 1 / 4,
        linetype = "dotted"
    ) +
    geom_hline(
        yintercept = 0.5,
        linewidth = 1 / 4,
        linetype = "dotted"
    ) +
    ggdist::geom_lineribbon(aes(order = lv),
        size = 0.5
    ) +
    labs(
        x = "Age (months)",
        y = "Probability of acquisition",
        colour = "Cognateness (phonological similarity)",
        fill = "Cognateness (phonological similarity)",
        linetype = "Cognateness (phonological similarity)"
    ) +
    scale_linetype_manual(values = rev(c("solid", "dashed", "dotdash"))) +
    scale_colour_grey(start = 0, end = 0) +
    scale_fill_grey(start = 0.85, end = 0.35) +
    scale_y_continuous(
        breaks = seq(0, 1, 0.25),
        limits = c(0, 1)
    ) +
    scale_x_continuous(breaks = seq(0, 50, 5)) +
    theme(
        legend.position = "top",
        legend.box = "vertical",
        legend.title.align = 1,
        legend.justification = "right",
        legend.direction = "horizontal",
        legend.key.size = unit(1, "cm"),
        legend.key.height = unit(1, "cm"),
        axis.text.x = element_text(size = 9),
        panel.grid = element_blank(),
        panel.border = element_rect(
            fill = NA,
            colour = "black",
            linewidth = 0.75
        )
    )
```

>>>>

```{r fig-marginal}
#| label: fig-marginal
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 4.5
#| out-width: 100%
#| eval: true
#| fig-cap: "Posterior marginal effects. Lines and error bands correspond to the mean and 95% credible interval of the posterior-predicted means. Different shades of grey indicate different levels of cognateness (phonological similarity). Predictions are presented separately for different degrees of word-form exposure index: little exposure to the word-form, mean exposure, and high exposure). Predictions for Comprehension are shown on top and predictions for Comprehension and Production are shown on the bottom. In-sample predictions lie inside the yellow rectangles. For reference, we indicate the 50% chance level of word acquisition (horizontal yellow lines), and the mean age of the sample (vertical yellow lines)."
fig_data <- model_epreds |>
    ungroup() |>
    reframe(
        .median = mean(.value),
        .lower = tidybayes::qi(.value, .width = 0.95)[, 1],
        .upper = tidybayes::qi(.value, .width = 0.95)[, 2],
        .by = c(ends_with("_std"), .category)
    ) |>
    mutate(
        age = (age_std * sd(responses$age)) + mean(responses$age),
        exposure = factor(exposure_std,
            levels = unique(exposure_std),
            labels = c(
                "Low exposure (-1 SD)",
                "Mean exposure",
                "High exposure (+1 SD)"
            ),
            ordered = TRUE
        ),
        lv = factor(lv_std,
            levels = unique(lv_std),
            labels = paste0(c(0, 50, 100), "%"),
            ordered = TRUE
        ),
        .category = ifelse(.category == "Understands",
            "Comprehension",
            "Production"
        )
    )
fig_data |>
    ggplot(aes(age, .median,
        ymin = .lower,
        ymax = .upper,
        colour = lv,
        fill = lv,
        linetype = lv
    )) +
    facet_grid(.category ~ exposure) +
    annotate(
        geom = "rect",
        xmin = min(responses$age),
        xmax = max(responses$age),
        ymin = -Inf,
        ymax = Inf,
        fill = "orange",
        alpha = 1 / 4,
        linetype = "dotted"
    ) +
    annotate(
        geom = "text",
        x = min(responses$age),
        y = 1,
        hjust = 0,
        vjust = 0.9,
        label = "Observed\nage range",
        size = 2
    ) +
    geom_vline(
        xintercept = mean(responses$age),
        linewidth = 2 / 4,
        alpha = 0.5,
        colour = "orange"
    ) +
    geom_hline(
        yintercept = 0.5,
        linewidth = 2 / 4,
        alpha = 0.5,
        colour = "orange"
    ) +
    ggdist::geom_lineribbon(aes(order = lv),
        size = 0.5
    ) +
    labs(
        x = "Age (months)",
        y = "Probability of acquisition",
        colour = "Cognateness (phonological similarity)",
        fill = "Cognateness (phonological similarity)",
        linetype = "Cognateness (phonological similarity)"
    ) +
    scale_linetype_manual(values = rev(c("solid", "dashed", "dotdash"))) +
    scale_colour_grey(start = 0, end = 0) +
    scale_fill_grey(start = 0.85, end = 0.35) +
    scale_y_continuous(
        breaks = seq(0, 1, 0.25),
        limits = c(0, 1)
    ) +
    scale_x_continuous(breaks = seq(0, 50, 5)) +
    theme(
        legend.position = "top",
        legend.box = "vertical",
        legend.title.align = 1,
        legend.justification = "right",
        legend.direction = "horizontal",
        legend.key.size = unit(1, "cm"),
        legend.key.height = unit(1, "cm"),
        axis.text.x = element_text(size = 9),
        panel.grid = element_blank(),
        panel.border = element_rect(
            fill = NA,
            colour = "black",
            linewidth = 0.75
        )
    )
```
